### 2016-02-03 doc/tutorial/detailed.Rmd
snapshot
fix bvm wrapper

This means that the wrapper for your SVM was not found, therefore no object was created, and the findSoftware could not be executed, because it is simply not there. Double check that adding the SVM package works for you, e.g. by enabling verbose mode.
'

>>>>

This means that the wrapper for your SVM was not found, therefore no object was created, and the findSoftware could not be executed, because it is simply not there. Double check that adding the SVM package works for you, e.g. by enabling verbose mode.

## Something like basename(trainBinaryPath) : a character vector argument expected happened.

(FIXME actually). The software was not found, so there is no trainBinaryPath in the SVM object.
'
## Reading my SVM model (or data file) yields a 0x0 matrix?

Make sure the model has the correct line endings. On windows you need 0x0d0a, else, if the model/data file has e.g. linux endings (0x0a), these will not be correctly read, that is the whole file will be read as one line, confusing the reader.
